---
title: "Dashboard"
format: 
  dashboard:
    orientation: rows
---

# Marketing Performance Dashboard

This dashboard presents a simple overview of marketing campaign performance across different digital channels.

## Row

### Value Box

```{r}
#| echo: false

library(bslib)

value_box(
  title = "Total Revenue",
  value = "$236K",
  theme = "primary"
)
```

### Value Box

```{r}
#| echo: false

library(bslib)

value_box(
  title = "Conversions",
  value = "4,850",
  theme = "success"
)
```

### Value Box

```{r}
#| echo: false

library(bslib)

value_box(
  title = "Marketing Spend",
  value = "$75K",
  theme = "warning"
)
```

## Row

### Revenue by Channel

```{r}
#| echo: false

library(ggplot2)

marketing_data <- data.frame(
  Channel = c("Email", "Facebook", "Google", "Instagram", "LinkedIn"),
  Revenue = c(28000, 45000, 61000, 52000, 47000)
)

ggplot(marketing_data, aes(x = Channel, y = Revenue)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Revenue by Marketing Channel",
    x = "Channel",
    y = "Revenue"
  )
```

### Monthly Website Traffic

```{r}
#| echo: false

traffic_data <- data.frame(
  Month = c("Jan", "Feb", "Mar", "Apr", "May", "Jun"),
  Visitors = c(1200, 1800, 2400, 3000, 3600, 4200)
)

ggplot(traffic_data, aes(x = Month, y = Visitors, group = 1)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Monthly Website Traffic",
    x = "Month",
    y = "Visitors"
  )
```

# Key Insights

-   Google generated the highest revenue among all channels.
-   Website traffic steadily increased over six months.
-   Social media channels contributed significantly to conversions.
-   Marketing performance improved consistently over time.
